---
title: ""
author: ""
date: ""
output: 
  md_document:
    variant: markdown_github
---
```{r,echo=FALSE}
knitr::opts_chunk$set(comment=".", fig.path="img/README-")
```



#modmrg

A package of models in `mrgsolve` format.

## Installation
```{r,eval=FALSE}
devtools::install_github("metrumresearchgroup/modmrg", subdir="rdev")
```
## Dependencies
`modmrg` depends on `mrgsolve`.  __NOTE__: we are still working out the necessary policies to make sure that `modmrg` is compatible 
with `mrgsolve`.  For now, it is best to use the latest dev versions of both packages.

## Models
1. PK: 1, 2, 3 compartment
    * All with dual-absorption and linear + non-linear elimination pathways
1. PD (all with 2-cmt PK): 
    * Indirect response type 1, 2, 3, 4
    * Direct EMAX model 
    * Effect compartment model
1. TMDD
1. Viral dynamic 1- and 2-strain models

## Help
```{r,eval=FALSE}

?modmrg


```


## Examples

### 2-Compartment PK model
```{r}
library(modmrg)

mod <- pk2cmt()

mod

param(mod)

init(mod)

mod %>%
  ev(amt=250, ii=48, addl=10) %>% 
  mrgsim(end=1000 )%>% 
  plot
```


### Indirect response model
```{r}
mod <- irm1()
see(mod)

mod %>% 
  param(CL=0.5, n=2.5, IMAX=0.85) %>%
  ev(amt=750) %>% 
  Req(RESP) %>% 
  knobs(IC50=seq(5,55,10), delta=0.1, end=96) %>%
  plot
  
```


### PK model with analytical solution (not based on ODEs)
```{r}
mod <- modmrg::pkmodel(ncmt=2) %>% param(Q=1, V2=8) %>% Req(CP)
mod %>% ev(amt=1000,rate=1000/100) %>% mrgsim(end=336) %>% plot
```

